---
title: "Volcanic Eruptions around the world"
author: "Jonathan Wharton"
date: "24/10/2021"
output: 
  ioslides_presentation:
    css: styles.css
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(readxl)
```

## The Assignment

The goals of this assignment were to:

1. create an original Shiny application and deploy it.
2. create a reproducible pitch presentation about the application.

#### This Shiny Application allows users to visualize volcanic eruption data and get insights to where different regions of the world have had many volcanic eruptions.

### Links
[The Shiny application](https://johnny-wharton.shinyapps.io/volcanoes/) <br>
[The code that created the application](https://github.com/johnnyjw/ddp/tree/main/4_ass/volcanoes)   (right click to open link in new tab)

## The Data
* This dataset comes from the National Geophysical Data Center / World Data Service. 
* Each row in the dataset is a Country/Region, a year, and the number of significant volcano eruptions in that year.
* A significant eruption is classified as one that meets at least one of the following criteria: caused fatalities, caused moderate damage (approximately $1 million or more), with a Volcanic Explosivity Index (VEI) of 6 or larger, caused a tsunami, or was associated with a major earthquake.
* The timespan of the data is from 1750 BCE to 2017 AD.
* The completeness of the data for earlier years is expected to be very low.

## The Application
### What does the application do?
* Shows the total number of Significant Volcanic eruptions by Country/Region or by Continent and see where most of the eruptions have occured.
* Allows the user to control the timespan for which the total number of Significant Volcanic Eruptions are calculated.
* Allows the user to limit the top number of countries/regions or continents to display on the graph and table.

### Why is this useful?
* Allows the user to get quick insights into where in the world there are volcanic eruptions
*     How incomplete is earlier data?
*     Have the same parts of the world consistently had the most eruptions across time?
*     Where have the most eruptions occurred during certain timespans?


## Data Sample

Below is a sample of the volcanic eruptions dataset, in this case the last few rows of data from Indonesia. 

```{r erupt, echo=TRUE}
cont <- read_excel('continents.xlsx')
erupt <- read.csv('significant-volcanic-eruptions.csv') %>% 
  rename('erupt' = "Number.of.significant.volcanic.eruptions..NGDC.WDS.") %>% 
  left_join(cont %>% select(Code, Continent), by = "Code") %>% 
  filter(Code=="IDN")
tail(erupt)
```
[The full code for the application is here](https://github.com/johnnyjw/ddp/tree/main/4_ass/volcanoes)
