---
title: "googleVis"
author: "jjw"
date: "18/01/2021"
output: html_document
---

* The R function creates an HTML page
* The HTML page calls Google Charts
* The result is an interactive HTML graphic



## Example
## Chart
```{r gv, results="asis",, cache=TRUE}

suppressPackageStartupMessages(library(googleVis))
G <- gvisGeoChart(Exports, locationvar="Country",
                  colorvar="Profit", options=list(width=600, height=400))
#print(G, "chart")


```

## Charts in googleVis



```{r chart2}
G2 <- gvisGeoChart(Exports, locationvar="Country",
                  colorvar="Profit", options=list(width=600, height=400, region = "150"))
```

## Line chart

```{r linie}
df <- data.frame(label=c("US", "GB", "BR"), val1=c(1,3,4), val2=c(23,12,32))
Line <- gvisLineChart(df, xvar="label", yvar=c("val1", "val2"),
                      options=list(title="Hello World", legend="bottom",
                                   titleTextStyle="{color:'red', fontSize:18)",
                                   vAxis="{gridlines:{color:'red', count:3}}",
                                   hAxis="{title:'My Label', titleTextStyle:{color:'blue'}}",
                                   series="[{title:'Value 1 (%)', format:'##, ######%'}]",
                                   curveType="function", width=500, height=300
                      ))
                 
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


,
                      vAxis="{gridlines:{color:'red', count:3}}",
                      hAxis="{title:'My Label', titleTextStyle:{color:'blue}}",
                      series="[{title:'Value 1 (%)', format:'##, ######%'}]",
                      curveType="function", width=500, height=300
