---
title: "My Fancy Presentation"
author: "Johnny Wharton"
date: "25 January 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My New Slide
Some content

***
A slide without a title 

## A Slide Header

### A top level subheading

#### A second level subheading


## Another Title

- Bullet one
- Bullet two

1. Item a
2. Item b

## My New Slide four

Plain text

*italicised text*

**Bold text**

`for (i %in% 1:10)`

## Another slide with code
```{r}
head(mtcars)
```

## mooooorre
```{r, comment=""}
head(mtcars)
```

## mooooorre more
```{r, comment="", echo=TRUE}
head(mtcars)
```


## mooooorre more again
```{r, comment="", echo=TRUE, eval=FALSE,}
head(mtcars)
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

